\documentclass[a4paper,11pt,twocolumn]{ltjsarticle}

\usepackage{luacode,luatexbase}
\usepackage[no-math,deluxe,expert,haranoaji]{luatexja-preset}

%%% for debug
\usepackage{nodetree}
\NodetreeRegisterCallback{:post_linebreak_filter:}
%%%

\newcommand{\luline}[1]{\bgroup\attribute100=100 #1\egroup}

\directlua{%
local setrcolor = node.new("whatsit","pdf_colorstack")
setrcolor.data = "1.0 1.0 0.45 rg"
local resetcolor = node.new("whatsit","pdf_colorstack")
resetcolor.data = "0 0 0 rg"

local ulines = function (head, group)
  for list in node.traverse_id(node.id("hlist"), head) do
    for item in node.traverse(list.head) do
      if item.id == node.id("glyph") or item.id == node.id("glue") then
        if node.has_attribute(item, 100) == 100 then
          local r = node.new("rule")
          local k = node.new("kern")
          r.height = 100000
          r.width = item.width
          k.kern = -item.width
          if item.id == node.id("glue") then 
            r.width = r.width + item.stretch + item.shrink + 50000
            k.kern = k.kern - item.stretch - item.shrink - 50000
          end
          if item.width > 0 then
          list.head, new = node.insert_before(list.head, item, node.copy(setrcolor))
          list.head, new = node.insert_before(list.head, item, r)
          list.head, new = node.insert_before(list.head, item, node.copy(resetcolor))
          list.head, new = node.insert_before(list.head, item, k)
          end
          item = item.next
        end
      end
     end
   end
   return head
end
luatexbase.add_to_callback ("post_linebreak_filter",ulines,"pushftn")
}

\begin{document}

Hell\luline{o W}orld! Hello World! Hello World! Hello World! Hello World! \luline{Hello World! Hello World! Hello World! Hello World! Hello World! Hello World! }Hello World! Hello World! Hello World! 

いろはにほへといろはにほへといろはにほへといろはにほへといろはにほへと\luline{いろはにほへといろはにほへといろはにほへといろはにほへと}いろはにほへといろはにほへといろはにほへといろはにほへと

\end{document}